A Step-Indexed Logic in Agda

### 2023-07-24 papers/July2024/paper.tex
rough draft

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Step-indexed logical relations are an important tool in the
  metatheory of programming
  languages~\citep{Appel:2001aa,Ahmed:2006aa}, and their application
  can be streamlined by use of step-indexed modal logics such as
  LSLR~\citep{Dreyer:2011wl}.  This paper describes an embedding of a
  step-indexed modal logic in Agda and its application to a semantic
  type safety proof for the Simply-Typed Lambda Calculus extended with
  recursive functions.
\end{abstract}

@@

\input{latex/cpp2024/StepIndexedLogic.tex}

\input{latex/cpp2024/STLC.tex}
\input{latex/cpp2024/STLCBind.tex}
\input{latex/cpp2024/STLCSafe.tex}

@@

\section*{Appendix}

\input{latex/cpp2024/STLCDeterministic.tex}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Step-indexed logical relations are an important tool in the
  metatheory of programming
  languages~\citep{Appel:2001aa,Ahmed:2006aa}, and their application
  can be streamlined by use of step-indexed modal logics such as
  LSLR~\citep{Dreyer:2011wl}.  This paper describes a mechanization of
  a step-indexed modal logic in the Agda proof assistant and its
  application to a semantic type safety proof for the Simply-Typed
  Lambda Calculus extended with recursive functions. The step-indexed
  logic supports guarded recursive predicates via the later modality
  and provides a fixpoint theorem adapted from \citet{Appel:2001aa}.
\end{abstract}

@@

\input{latex/July2024/StepIndexedLogic.tex}

\input{latex/July2024/STLC.tex}
\input{latex/July2024/STLCBind.tex}
\input{latex/July2024/STLCSafe.tex}

@@

\appendix
\addcontentsline{toc}{section}{Appendix}
\section*{Appendix}

\input{latex/July2024/STLCDeterministic.tex}
